### 2024-05-05 paper/sec/3_methods.tex

\indent Another point of interest is that poses would have a low “change in body position” score. Going back to the 
corner detection analogy, poses are analogous to a flat area within an  image, yet they arguably define a 
person’s physical actions more than the brief moments of highest “change in body position”. Thus, to extract 
poses from angles, we actually apply non-minimum suppression (instead of the Harris Corner Detector’s 
non-maximum suppression) after calculating the Euclidean Distance between angles in adjacent frames.

\indent Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
significant “change in body position”. Arguably, a gesture would take place for all the frames between 
two poses, not just for moments of the fastest “change in body position”. However, because we applied a 
threshold that selects only a subset of the most significant poses, the above definition may cause multiple 
gestures to be recognized as one, so we have currently defined a gesture to be three consecutive frames of 
significant change in angles. (However, it could be interesting to explore modified algorithms for detecting 
poses and gestures in future work.)

>>>>

\indent Another point of interest is that poses would have a low “change in body position” score. Going back to the 
corner detection analogy, poses are analogous to a flat area within an  image, yet they arguably define a 
person’s physical actions more than the brief moments of highest “change in body position.” Thus, to extract 
poses from angles, we actually apply non-minimum suppression (instead of the Harris Corner Detector’s 
non-maximum suppression) after calculating the Euclidean Distance between angles in adjacent frames.

\indent Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
significant “change in body position.” Arguably, a gesture would take place for all the frames between 
two poses, not just for moments of the fastest “change in body position.” However, because we applied a 
threshold that selects only a subset of the most significant poses, the above definition may cause multiple 
gestures to be recognized as one, so we have currently defined a gesture to be three consecutive frames of 
significant change in angles. (However, it could be interesting to explore modified algorithms for detecting 
poses and gestures in future work.)

### 2024-05-05 paper/sec/6_conclusion.tex
Update 6_conclusion.tex

\subsection{Limitations}
\indent Although we believe our project proves large progress, it did 
come with its fair share of limitations. As previously stated the camera 
angle between the videos must be the same, otherwise the scores will not 
accurately reflect their performance. This is due to the fact that our 
Gesture Detection algorithm is overly simple.

\indent Another major limitation we faced in the creation of the project 
is the time bottleneck from OpenPose. Due to our restrictions with GPU 
access, we were forced to downscale the data we processed; either 
through resolution or duration. Downscaling the resolution proved to 
reduce the most time, however, it also produced questionable keypoints. 
Thus, for the purpose of testing, we were forced to process shorter 
videos at full resolution, in order to get the most accurate keypoints 
from OpenPose; this resulted in a vast time limitation as a 16-second 
video took 34 minutes to process.

@@

\indent The final update would be to expand the project’s scope to 
other physical activities. Specifically, we would like to focus on 
dance. The project would be able to determine a dancer’s accuracy, and 
offer many practice dance movements from various genres that the 
dancer can practice with. Another implication could be martial arts, 
which would work in the same way that physical therapy and dance would, 
but be tailored for any unexpected specifications that martial arts 
requires.

>>>>

\subsection{Limitations}
\indent Although we believe our project proves great advancement, it did 
come with its fair share of limitations. As previously stated the camera 
angle between the videos must be the same, otherwise the scores will not 
accurately reflect their performance. This is due to the fact that our 
Gesture Detection algorithm is overly simple.

\indent Another major limitation we faced in the creation of the project 
is the time bottleneck from OpenPose. Due to our restrictions with GPU 
access, we were forced to downscale the data we processed, either 
through resolution or duration. Downscaling the resolution proved to 
reduce the most time; however, it also produced questionable keypoints. 
Thus, for the purpose of testing, we were forced to process shorter 
videos at full resolution, in order to get the most accurate keypoints 
from OpenPose; this resulted in a vast time limitation as a 16-second 
video took 34 minutes to process.

@@

\indent The final update would be to expand the project’s scope to 
other physical activities. Specifically, we would like to focus on 
dance. The project would be able to determine a dancer’s accuracy and 
offer many practice dance movements from various genres that the 
dancer can practice with. Another implication could be martial arts, 
which would work in the same way that physical therapy and dance would, 
but be tailored for any unexpected specifications that martial arts 
requires.
